Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-16 demystify.tex
updates

\section{CV}
\sectioninfo{Highlight and summarize major achievements, e.g., Publications, Programming Awards}

@@

\part{After You Apply}\label{part:after-apply}
\chapter{Interview and the Waiting Game}\label{chap:interview}
\chapterinfo{Getting an interview is typically a good sign; but no interview does not mean rejection}

@@

\chapter{Dealing with Rejection}\label{chap:not-accepted}
\chapterinfo{Rejection is common and part of academia.  Common reasons for rejection include aiming too high, not a good fit, or bad luck. Learn from it and try again.}

>>>>

\section{CV}
\sectioninfo{Highlight and summarize major achievements such as major publications and competitive programming awards.}

@@

\part{After You Apply}\label{part:after-apply}
\chapter{Interview and the Waiting Game}\label{chap:interview}
\chapterinfo{Getting an interview is typically a good sign; but no interview does not mean rejection.}

@@

\chapter{Dealing with Rejection}\label{chap:not-accepted}
\chapterinfo{Rejection is part of academia.  Common reasons for rejection include aiming too high, not a good fit, and bad luck.  Do not take rejection personally. Learn from it and try again.}
